\chapter{Ethics Policy}\label{G:EtP}
\CommonIntroduction
\section{Overview}
\CompanyName{} is committed to protecting employees, partners, vendors and the company from illegal or damaging actions by individuals, either knowingly or unknowingly.  
When \CompanyName{} addresses issues proactively and uses correct judgment, it will help set us apart from competitors.

\CompanyName{} will not tolerate any wrongdoing or impropriety at any time.  
\CompanyName{} will take the appropriate measures act quickly in correcting the issue if the ethical code is broken.  
\section{Purpose}
The purpose of this policy is to establish a culture of openness, trust\oxford{} and to emphasize the employee's and consumer's expectation to be treated to fair business practices.  
This policy will serve to guide business behavior to ensure ethical conduct.  
Effective ethics is a team effort involving the participation and support of every \CompanyName{} employee.  
All employees should familiarize themselves with the ethics guidelines that follow this introduction.
\section{Scope}
This policy applies to employees, contractors, consultants, temporaries, and other workers at \CompanyName{}, including all personnel affiliated with third parties.
\section{Policy}
\subsection{Executive Commitment to Ethics}
\begin{enumerate}
\item 
Senior leaders and executives within \CompanyName{} must set a prime example.  
In any business practice, honesty and integrity must be top priority for executives.
\item 
Executives must have an open door policy and welcome suggestions and concerns from employees.  
This will allow employees to feel comfortable discussing any issues and will alert executives to concerns within the work force.
\item
Executives must disclose any conflict of interests regard their position within \CompanyName{}.
\end{enumerate}
\subsection{Employee Commitment to Ethics}
\begin{enumerate}
\item 
\CompanyName{} employees will treat everyone fairly, have mutual respect, promote a team environment and avoid the intent and appearance of unethical or compromising practices.
\item 
Every employee needs to apply effort and intelligence in maintaining ethics value.
\item 
Employees must disclose any conflict of interests regard their position within \CompanyName{}.
\item 
Employees will help \CompanyName{} to increase customer and vendor satisfaction by providing quality products and timely response to inquiries.
\item 
Employees should consider the following questions to themselves when any behavior is questionable:
\begin{itemize}
\item 
Is the behavior legal?
\item 
Does the behavior comply with all appropriate \CompanyName{} policies?
\item 
Does the behavior reflect \CompanyName{} values and culture?
\item 
Could the behavior adversely affect company stakeholders?
\item 
Would you feel personally concerned if the behavior appeared in a news headline?
\item 
Could the behavior adversely affect \CompanyName{} if all employees did it?
\end{itemize}
\end{enumerate}
\subsection{Company Awareness}
\begin{enumerate}
\item 
Promotion of ethical conduct within interpersonal communications of employees will be rewarded.
\item 
\CompanyName{} will promote a trustworthy and honest atmosphere to reinforce the vision of ethics within the company.
\end{enumerate}
\subsection{Maintaining Ethical Practices}
\begin{enumerate}
\item
\CompanyName{} will reinforce the importance of the integrity message and the tone will start at the top.  
Every employee, manager, \ins{and} director needs consistently maintain an ethical stance and support ethical behavior.
\item
Employees at \CompanyName{} should encourage open dialogue, get honest feedback\oxford{} and treat everyone fairly, with honesty and objectivity.
\item
\CompanyName{} has established a best practice disclosure committee to make sure the ethical code is delivered to all employees and that concerns regarding the code can be addressed.
\item
Employees are required to \del{re}certify their compliance to the \hyperref[E:EtP]{ethics policy} on an annual basis. 
\end{enumerate}
\subsection{Unethical Behavior}
\begin{enumerate}
\item
\CompanyName{} will avoid the intent and appearance of unethical or compromising practice in relationships, actions\oxford{} and communications.  
\item
\CompanyName{} will not tolerate harassment or discrimination.
\item
Unauthorized use of company trade secrets \oldnew{\&}{and} marketing, operational, personnel, financial, source code, \oldnew{\&}{and} technical information integral to the success of our company will not be tolerated.
\item
\CompanyName{} will not permit impropriety at any time and we will act ethically and responsibly in accordance with laws.
\item
\CompanyName{} employees will not use corporate assets or business relationships for personal use or gain.
\end{enumerate}
\section{Policy Compliance}
\subsection{Compliance Measurement}
The \textsl{Employee Resource Team} will verify compliance to this policy through various methods, including but not limited to, business tool reports, internal and external audits, and feedback. 
\subsection{Exceptions}
None. 
\subsection{Non-Compliance}
An employee found to have violated this policy may be subject to disciplinary action, up to and including termination of employment. 
\section{Related Standards, Policies and Processes}
None.
\section{Definitions and Terms}
None.
\CommonRevisionHistory