\chapter{Software Installation Policy}
\section{Overview}
Allowing employees to install software on company computing devices opens the organization up to unnecessary exposure.  
Conflicting file versions or \glspl{dll} which can prevent programs from running, the introduction of malware from infected installation software, unlicensed software which could be discovered during audit\oxford{} and programs which can be used to hack the organization's network are\ins{ all} examples of \del{the }problems that can be introduced when employees install software on company equipment.
\section{Purpose}
The purpose of this policy is to outline the requirements around installation software on \CompanyName{}-owned computing devices.  
To minimize the risk of loss of program functionality, the exposure of sensitive information contained within \CompanyName{}'s computing network, the risk of introducing malware, and the legal exposure of running unlicensed software.
\section{Scope}
This policy applies to all \CompanyName{} employees, contractors, vendors\oxford{} and agents with \del{a }\CompanyName{}-owned mobile devices.  
This policy covers all computers, servers, \smartphone{}s, tablets\oxford{} and other computing devices operating within \CompanyName{}.
\section{Policy}
\begin{itemize}
\item
Employees may not install software on \CompanyName{}'s computing devices operated within the \CompanyName{} network.  
\item
Software requests must first be approved by the requester's manager and then be made to the \gls{it} department or help desk in writing or via \email.  
\item
Software must be selected from an approved software list\oldnew{, }{ and} maintained by the \gls{it} department, unless no selection on the list meets the requester's need.  
\item
The \gls{it} department will obtain and track the licenses, test new software for conflict and compatibility, and perform the installation.
\end{itemize}
\CommonPolicyCompliance
\section{Related Standards, Policies\oxford{} and Processes}
None.
\section{Definitions and Terms}
None.
\CommonRevisionHistory

