\chapter{Acquisition Assessment Policy}\label{NS:AAP}
\CommonIntroduction
\section{Overview}
The process of integrating a newly acquired company can have a drastic impact on the security poster of either the parent company or the child company.  
The network and security infrastructure of both entities may vary greatly and the workforce of the new company may have a drastically different culture and tolerance to openness.  
The goal of the security acquisition assessment and integration process should include:
\begin{itemize}
\item
Assess company's security landscape, posture, and policies
\item
Protect both \CompanyName{} and the acquired company from increased security risks
\item 
Educate acquired company about \CompanyName{} policies and standard
\item
Adopt and implement \CompanyName{} security policies and standards
\item
Integrate acquired company
\item
Continuous monitoring and auditing of the acquisition
\end{itemize}
\section{Purpose}
The purpose of this policy is to establish \gls{infosec} responsibilities regarding corporate acquisitions, and define the minimum security requirements of an \gls{infosec} acquisition assessment.
\section{Scope}
This policy applies to all companies acquired by \CompanyName{} and pertains to all systems, networks, laboratories, test equipment, hardware, software and firmware, owned and/or operated by the acquired company.
\section{Policy}
\subsection{General}
Acquisition assessments are conducted to ensure that a company being acquired by \CompanyName{} does not pose a security risk to corporate networks, internal systems, and/or confidential/sensitive information.  
The \gls{infosec} Team will provide personnel to serve as active members of the acquisition team throughout the entire acquisition process.  
The \gls{infosec} role is to detect and evaluate information security risk, develop a remediation plan with the affected parties for the identified risk, and work with the acquisitions team to implement solutions for any identified security risks, prior to allowing connectivity to \CompanyName{}'s networks.  
Below are the minimum requirements that the acquired company must meet before being connected to the \CompanyName{} network. 
\subsection{Requirements}
\subsubsection{Hosts}
\begin{enumerate}
\item
All hosts (servers, desktops, laptops) will be replaced or re-imaged with a \CompanyName{} standard image or will be required to adopt the minimum standards for end user devices.
\item
Business critical production servers that cannot be replaced or re-imaged must be audited and a waiver granted by \gls{infosec}.
\item
All PC based hosts will require \CompanyName{} approved virus protection before the network connection. 
\end{enumerate}
\subsubsection{Networks}
\begin{enumerate}
\item
All network devices will be replaced or re-imaged with a \CompanyName{} standard image. 
\item
Wireless network access points will be configured to the \CompanyName{} standard. 
\end{enumerate}
\subsubsection{Internet}
\begin{enumerate}
\item
All Internet connections will be terminated. 
\item
When justified by business requirements, air-gapped Internet connections require \gls{infosec} review and approval. 
\end{enumerate}
\subsubsection{Remote Access}
\begin{enumerate}
\item
All remote access connections will be terminated. 
\item
Remote access to the production network will be provided by \CompanyName{}.
\end{enumerate}
\subsubsection{Labs}
\begin{enumerate}
\item 
Lab equipment must be physically separated and secured from non-lab areas. 
\item 
The lab network must be separated from the corporate production network with a firewall between the two networks. 
\item 
Any direct network connections (including analog lines, \gls{isdn} lines, T1, \etc) to external customers, partners, \etc, must be reviewed and approved by the \gls{labsec}.
\item 
All acquired labs must meet with \gls{labsec} \hyperref[SS:LSP]{lab policy}, or be granted a waiver by \gls{labsec}. 
\item 
In the event the acquired networks and computer systems being connected to the corporate network fail to meet these requirements, the \CompanyName{} \gls{cio} must acknowledge and approve of the risk to \CompanyName{}'s networks 
\end{enumerate}
\CommonPolicyCompliance
\section{Related Standards, Policies\oxford{} and Processes}
None.
\CommonDefinitionsAndTerms
\begin{itemize}
\item 
Business Critical Production Server
\end{itemize}
\CommonRevisionHistory