\chapter{Router and Switch Security Policy}\label[NS:RaSSP]
\CommonIntroduction
\section{Overview}
See \see{NS:RaSSP:Pu}
\section{Purpose}\label{NS:RaSSP:Pu}
This document describes a required minimal security configuration for all routers and switches connecting to a production network or used in a production capacity at or on behalf of \CompanyName{}.
\section{Scope}
All employees, contractors, consultants, temporary\oxford{} and other workers at \oldnew{Cisco}{\CompanyName{}} and its subsidiaries must adhere to this policy.  
All routers and switches connected to \oldnew{Cisco}{\CompanyName{}} production networks are affected.
\section{Policy}
Every router must meet the following configuration standards:
\begin{enumerate}
\item
No local user accounts are configured on the router.  
Routers and switches must use \gls{tacacsp} for all user authentication.
\item
The enable password on the router or switch must be kept in a secure encrypted form.  
The router or switch must have the enable password set to the current production router/switch password from the device's support organization.
\item
The following services or features must be disabled:
\begin{enumerate}
\item
\gls{ip} directed broadcasts 
\item
Incoming packets at the router/switch sourced with invalid addresses such as \RFC{1918} addresses
\item
\gls{tcp} small services 
\item
\gls{udp} small services 
\item
All source routing and switching
\item
All web services running on router
\item
Cisco discovery protocol on Internet connected interfaces
\item
\gls{telnet}, \gls{ftp}, and \gls{http} services
\item
Auto-configuration
\end{enumerate}
\item
The following services should be disabled unless a business justification is provided:
\begin{enumerate}
\item 
Cisco discovery protocol and other discovery protocols
\item 
Dynamic trunking
\item 
Scripting environments, such as the \gls{tcl} shell
\end{enumerate}
\item
The following services must be configured:
\begin{enumerate}
\item 
Password-encryption
\item
\gls{ntp} configured to a corporate standard source
\end{enumerate}
\item
All routing updates shall be done using secure routing updates.
\item
Use corporate standardized \gls{snmp} community strings.  
Default strings, such as public or private must be removed.  
\gls{snmp} must be configured to use the most secure version of the protocol allowed for by the combination of the device and management systems.
\item
\gls{acl}s must be used to limit the source and type of traffic that can terminate on the device itself.
\item
\gls{acl}s for transiting the device are to be added as business needs arise. 
\item
The router must be included in the corporate enterprise management system with a designated \gls{ptoc}. 
\item
Each router must have the following statement presented for all forms of login whether remote or local:
\begin{quote}\ttfamily{}UNAUTHORIZED ACCESS TO THIS NETWORK DEVICE IS PROHIBITED.  You must have explicit permission to access or configure this device.  All activities performed on this device may be logged\del{,} and violations of this policy may result in disciplinary action\oldnew{, and}{ and/or} may be reported to law enforcement.  There is no right to privacy on this device.  Use of this system shall constitute consent to monitoring.
\end{quote}
\item
\gls{telnet} may never be used across any network to manage a router, unless there is a secure tunnel protecting the entire communication path.  
\gls{ssh} version 2 is the preferred management protocol.
\item
Dynamic routing protocols must use authentication in routing updates sent to neighbors.  
Password hashing for the authentication string must be enabled when supported.
\item
The corporate router configuration standard will define the category of sensitive routing and switching devices, and require additional services or configuration on sensitive devices including:
\begin{enumerate}
\item
\gls{ip} access list accounting
\item
Device logging
\item
Incoming packets at the router sourced with invalid addresses, such as \RFC{1918} addresses, or those that could be used to spoof network traffic shall be dropped
\item
Router console and modem access must be restricted by additional security controls
\end{enumerate}
\end{enumerate}
\CommonPolicyCompliance
\section{Related Standards, Policies\oxford{} and Processes}
None.
\section{Definitions and Terms}
None.
\CommonRevisionHistory