\chapter{Wireless Communication Policy}
\CommonIntroduction
\section{Overview}
With the mass explosion of \smartphone{}s and tablets, pervasive wireless connectivity is almost a given at any organization.  
Insecure wireless configuration can provide an easy open door for malicious threat actors. 
\section{Purpose}
The purpose of this policy is to secure and protect the information assets owned by \CompanyName{}.  
\CompanyName{} provides computer devices, networks\oxford{} and other electronic information systems to meet missions, goals, and initiatives.  
\CompanyName{} grants access to these resources as a privilege and must manage them responsibly to maintain the confidentiality, integrity\oxford{} and availability of all information assets.

This policy specifies the conditions that wireless infrastructure devices must satisfy to connect to \CompanyName{} network.  
Only those wireless infrastructure devices that meet the standards specified in this policy or are granted an exception by the \gls{infosec} Department are approved for connectivity to a \CompanyName{} network.
\section{Scope}
All employees, contractors, consultants, temporary\oxford{} and other workers at \CompanyName{}, including all personnel affiliated with third parties that maintain a wireless infrastructure device on behalf of \CompanyName{} must adhere to this policy.  
This policy applies to all wireless infrastructure devices that connect to a \CompanyName{} network or reside on a \CompanyName{} site that provide wireless connectivity to endpoint devices including, but not limited to, laptops, desktops, cellular phones\oxford{} and tablets.  
This includes any form of wireless communication device capable of transmitting packet data. 
\section{Policy}
\subsection{General Requirements}\label{NS:WCP:Po:GR}
All wireless infrastructure devices that reside at a \CompanyName{} site and connect to a \CompanyName{} network, or provide access to information classified as \CompanyName{} Confidential\del{,} or above\ins{,} must: 
\begin{itemize}
\item
Abide by the standards specified in \oldnew{the Wireless Communication Standard}{\see{NS:WCS}}. 
\item
Be installed, supported\oxford{} and maintained by an approved support team.
\item
Use \CompanyName{} approved authentication protocols and infrastructure.
\item
Use \CompanyName{} approved encryption protocols.
\item
Maintain a hardware address (\gls{mac} address) that can be registered and tracked. 
\item
Not interfere with wireless access deployments maintained by other support organizations.
\end{itemize}
\subsection{Lab and Isolated Wireless Device Requirements}
All lab wireless infrastructure devices that provide access to \CompanyName{} Confidential or above, must adhere to \oldnew{section 4.1 above}{the \hyperref[N:WCP:Po:GR]{General Requirements}}.  
Lab and isolated wireless devices that do not provide general network connectivity to the \CompanyName{} network must: 
\begin{itemize}
\item
Be isolated from the corporate network (that is\ins{,} it must not provide any corporate connectivity) and comply with the \hyperref[SS:LSP]{Lab Security Policy}.
\item
Not interfere with wireless access deployments maintained by other support organizations. 
\end{itemize}
\subsection{Home Wireless Device Requirements}\label{NS:WCP:Po:HWDR}
\begin{enumerate}
\item
Wireless infrastructure devices that provide direct access to the \CompanyName{} corporate network, must conform to the Home Wireless Device Requirements as detailed in \oldnew{the Wireless Communication Standard}{\see{NS:WCS}}.
\item
Wireless infrastructure devices that fail to conform to the \hyperref[NS:WCP:Po:HWDR]{Home Wireless Device Requirements} must be installed in a manner that prohibits direct access to the \CompanyName{} corporate network.  
Access to the \CompanyName{} corporate network through this device must use standard remote access authentication.
\end{enumerate}
\CommonPolicyCompliance
\section{Related Standards, Policies\oxford{} and Processes}
\begin{itemize}
\item \see{SS:LSP}
\item \see{NS:WCS}
\end{itemize}

\section{Definitions and Terms}
\CommonDefinitionsAndTerms
\begin{itemize}
\item \gls{mac} Address
\end{itemize}
\CommonRevisionHistory
