\chapter{Wireless Communication Standard}\label{NS:WCS}
\CommonIntroduction
\section{Overview}
See \see{NS:WCS:Pu}.
\section{Purpose}\label{NS:WCS:Pu}
This standard specifies the technical requirements that wireless infrastructure devices must satisfy to connect to a \CompanyName{} network.  
Only those wireless infrastructure devices that meet the requirements specified in this standard or are granted an exception by the \gls{infosec} Team are approved for connectivity to a \CompanyName{} network.

Network devices including, but not limited to, hubs, routers, switches, firewalls, remote access devices, modems\oxford{} or \glspl{wap}, must be installed, supported\oxford{} and maintained by an \gls{infosec} approved support organization.  
Lab network devices must comply with \oldnew{the Lab Security Policy}{\see{NS:LSP}}.
\section{Scope}
All employees, contractors, consultants, temporary\oxford{} and other workers at \CompanyName{} and its subsidiaries, including all personnel that maintain a wireless infrastructure device on behalf of \CompanyName{}, must comply with this standard.  
This standard applies to wireless devices that make a connection the network and all wireless infrastructure devices that provide wireless connectivity to the network.

\gls{infosec} must approve exceptions to this standard in advance. 
\section{Standard}
\subsection{General Requirements}
All wireless infrastructure devices that connect to a \CompanyName{} network or provide access to \CompanyName{} Confidential, \CompanyName{} Highly Confidential\oxford{} or \CompanyName{} Restricted information must:
\begin{itemize}
\item
Use \gls{eapfast}, \gls{peap}\oxford{} or \gls{eaptls} as the authentication protocol.
\item
Use \gls{tkip} or \gls{aesys} protocols with a minimum key length of 128 bits.
\item
All Bluetooth devices must use Secure Simple Pairing with encryption enabled.
\end{itemize}
\subsection{Lab and Isolated Wireless Device Requirements}
\begin{itemize}
\item
Lab device \glspl{ssid} must be different from \CompanyName{} production device \glspl{ssid}.
\item
Broadcast of lab device \glspl{ssid} must be disabled.
\end{itemize}
\subsection{Home Wireless Device Requirements}
All home wireless infrastructure devices that provide direct access to a \CompanyName{} network, such as those behind \gls{ect} or hardware \gls{vpn}, must adhere to the following: 
\begin{itemize}
\item
Enable \gls{wpapsk}, \gls{eapfast}, \gls{peap}\oxford{} \gls{eaptls}.
\item
When enabling \gls{wpapsk}, configure a complex shared secret key (at least 20 characters) on the wireless client and the \gls{wap}.
\item
Disable broadcast of \gls{ssid}
\item
Change the default \gls{ssid} name
\item
Change the default login and password
\end{itemize}
\CommonPolicyCompliance
\section{Related Standards, Policies\oxford{} and Processes}
\begin{itemize}
\item \see{SS:LSP}
\end{itemize}
\CommonDefinitionsAndTerms
\begin{itemize}
\item \gls{aesys}
\item \gls{eapfast}
\item \gls{eaptls}
\item \gls{peap}
\item \gls{ssid}
\item \gls{tkip}
\item \gls{wpapsk}
\end{itemize}
\CommonRevisionHistory